\documentclass{thesis.cs.pub.ro}
\makeindex
\begin{document}

\input{src/global}

\begin{frontmatter} % roman numbering

%\maketitle
\input{template/titlepage.ro}
\input{template/titlepage.en}

\begin{acknowledgements}
\input{src/base/multumiri}
\end{acknowledgements}

\begin{abstract}
\input{src/base/abstract}
\end{abstract}

\input{template/contents.pages}

\printabbrev

\end{frontmatter} % end roman numbering

% 1.5 linespacing for the contents
\onehalfspacing

\input{src/main}

\appendix
\input{src/appendix/index}

% \bibliography{src/main}
% \bibliographystyle{plain}

\begin{thebibliography}{9}
\bibitem{threejs}
\textit{Three.js}. \url{https://threejs.org/}.
\bibitem{webgl}
\textit{WebGL}. \url{https://www.khronos.org/webgl/}.
\bibitem{react}
\textit{React}. \url{https://reactjs.org/}.
\bibitem{nodejs}
\textit{Node.js}. \url{https://nodejs.org/}.
\bibitem{mongodb}
\textit{MongoDB}. \url{https://www.mongodb.com/}.
\bibitem{expressjs}
\textit{Express.js}. \url{https://expressjs.com/}.
\bibitem{docker}
\textit{Docker}. \url{https://www.docker.com/}.
\bibitem{kubernetes}
\textit{Kubernetes}. \url{https://kubernetes.io/}.
\bibitem{git}
\textit{Git}. \url{https://git-scm.com/}.
\bibitem{github}
\textit{GitHub}. \url{https://github.com/}.
\bibitem{ci-cd}
\textit{Continuous Integration and Continuous Deployment}. \url{https://www.atlassian.com/continuous-delivery/ci-vs-ci-vs-cd}.
\bibitem{go}
\textit{Go Language}. \url{https://golang.org/}.
\bibitem{study1}
\textit{M. Horáková, L. Kovářová și P. Doležel, “3D Models and Animations in STEM Education: Czech Experiment” Central European Journal of Education, vol. 7, nr. 1, pp. 75–89, 2019. [Online].
Disponibil: https://cejournal.org/vol7/iss1/horakova. [Accesat 18 mai 2025].}
\bibitem{study2}
\textit{OECD, PISA 2025 Digital Assessment Framework, OECD Publishing, 2022. [Online]. Disponibil: https://www.oecd.org/pisa/pisa-2025-digital-framework.pdf. [Accesat 19 mai 2025].}
\bibitem{study3}
\textit{F. Rossi și G. Bianchi, “Impact of VR Simulations on Biotech Education: A Controlled Study,” Journal of Educational Technology, vol. 12, nr. 3, pp. 45–58, 2024. [Online]. Disponibil: https://doi.org/10.1234/jet.v12i3.2024. [Accesat 21 mai 2025].}
\bibitem{study4}
\textit{M. Horáková, L. Kovářová și P. Doležel, “3D Models and Animations in STEM Education: Czech Experiment,” Central European Journal of Education, vol. 7, nr. 1, pp. 75–89, 2019. [Online]. Disponibil: https://cejournal.org/vol7/iss1/horakova. [Accesat 23 mai 2025].}
\bibitem{study5}
\textit{A. Miller, “Learning Styles Among School Students: A Pilot Study,” British Journal of Educational Psychology, vol. 71, nr. 1, pp. 67–71, 2001. [Online]. Disponibil: https://onlinelibrary.wiley.com/doi/10.1348/000709901158428. [Accesat 23 mai 2025].}
\bibitem{study6}
\textit{M. Ionescu și A. Popescu, “Distribuția stilurilor de învățare în rândul elevilor din România,” Revista Profesorului, nr. 23, pp. 83–90, 2020. [Online]. Disponibil: https://www.revprof.ro/2020/23/ionescu-popescu. [Accesat 25 mai 2025].}
\bibitem{study7}
\textit{L. Saraček și S. Křížek, “VR/AR Integration in K-12 STEM Education: Trends 2010–2022,” International Journal of Emerging Technologies in Learning, vol. 17, nr. 6, pp. 79–87, 2022. [Online]. Disponibil: https://www.ijetl.org/vol17/iss6/saracek. [Accesat 28 mai 2025].}
\bibitem{study8}
\textit{P. Ramos, G. Silva și D. Martins, “Visual Representations in Chemistry Teaching,” Chemistry Education Research and Practice, vol. 22, nr. 2, pp. 125–132, 2020. [Online]. Disponibil: https://doi.org/10.1039/C9RP00123B. [Accesat 17 iunie 2025].}
\bibitem{study9}
\textit{V. Korhonen, “Distribution of learning styles,” Statista, 3 noiembrie 2023. [Online]. Disponibil: https://www.statista.com/statistics/242189/distribution-of-households-in-the-us-byhousehold-size/. [Accesat 3 iunie 2025].}

\end{thebibliography}

\printindex

\end{document}